Fifteen years of decentralization attempts

### 2014-03-24 paper.tex
Typoo

			\item The Tor network doesn't have the capacity to handle all the users that want privacy on the internet. According to the Tor Metrics project \cite{tormetricsprojectwebsite}, it takes about 6 seconds to download 1 MiB of data. Due to the fact that traffic travels over multiple Tor nodes, the total amount of transfered data in the network multiplies. This is illustrated in figure \ref{fig:hops}. By having $n$ hops, the amount of transfered traffic would be multiplied by $2(n+1)$. This means that a 1 GiB transfer, using only 1 hop, would actually cost the network 4 GiB. By increasing the amount of Onion Routing in the Tor network, the capacity is increased. Incentives such as LIRA \cite{jansen13lira} could make more users run an Onion Router, thus increasing the capacity of the network and making it faster.

>>>>

			\item The Tor network doesn't have the capacity to handle all the users that want privacy on the internet. According to the Tor Metrics project \cite{tormetricsprojectwebsite}, it takes about 6 seconds to download 1 MiB of data. Due to the fact that traffic travels over multiple Tor nodes, the total amount of transferred data in the network multiplies. This is illustrated in figure \ref{fig:hops}. By having $n$ hops, the amount of transferred traffic would be multiplied by $2(n+1)$. This means that a 1 GiB transfer, using only 1 hop, would actually cost the network 4 GiB. By increasing the amount of Onion Routing in the Tor network, the capacity is increased. Incentives such as LIRA \cite{jansen13lira} could make more users run an Onion Router, thus increasing the capacity of the network and making it faster.
